Re-examining cross-cultural similarity judgements using lexical co-occurrence

### 2023-01-20 code/4_paper/manuscript/manuscript_0119.Rmd
cogsci paper exchange

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("kableExtra")
library("irr")
require(agreement)

@@

# set the default ggplot theme 
theme_set(theme_classic(base_size = 7))

@@

```{r get exclusions data, include = F, cache = T}
df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv") %>%
  select(-X)
df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv") %>%
  select(-X)
df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv") %>%
  select(-X)
```

@@

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}

@@

@@

### Is responding in each cultural context best predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above. In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).

@@

plot.coeffs_cos <- ggplot(data = df.USVNCN_coeffs_cos, 
       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
                 position=position_dodge(.9)) +
  scale_y_reverse() + 
  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
#plot.coeffs_freq + 
  plot.coeffs_cos
```

@@

@@

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.align = "center", fig.cap="Proportion of thematic responses by country."}
#show violin plot
ggplot(df.country_filler,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = word1_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Word1 Chosen", 
       x = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
  theme(legend.position = "none")
```

```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", paged.print=TRUE}
# df.country_sum <- df.country %>%
#   group_by(country) %>%
#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
#             sd_theme_resp_percent = sd(theme_resp_percent))

@@

### Does lexical statistics for fillers predict responding in the corresponding cultural context?
<!-- #### Raw co-occurrences -->
<!-- ```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F} -->
<!-- # English  -->
<!-- fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue),  -->
<!--           data = df.filler %>% filter(country == "US",  -->
<!--                                !(cue_id %in% fillers_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.EN_US_filler) -->
<!-- fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3) -->

@@

@@

```{r xtable, results ="asis", fig.pos="H"}
US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
                             model = "2A",
                             type = "agreement",
                             unit = "average",
                             object = triad,
                             rater = subject,
                             score = responses_theme,
                             bootstrap = 0)

print(tab1, type="latex", comment = F, include.rownames = FALSE)
```

## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context

## 3. Demographic Exclusion Statistics
```{r results = "asis", fig.cap="Testing"}
df.demog_excl <- cbind(t(df.excl_US), t(df.excl_CN))
df.demog_excl <- cbind(df.demog_excl, t(df.excl_VN))

rownames(df.demog_excl) <-
  c("Country", "Ppts Finished", 
    "Excluded", 
    "After Exclusion", 
    "Non-Native Speakers", "EN Speakers", 
    "VI Speakers", "ZH Speakers", 
    "Lived Abroad", "Overseas Experience", 
    "After Exclusions")

colnames(df.demog_excl) <- df.demog_excl[1,]
df.demog_excl <- df.demog_excl[-1, ]

kbl(df.demog_excl, align = "c") %>%
  add_header_above(c(" " = 1, "Country" = 3)) %>%
  pack_rows(index = c(" " = 1, "Attention Check Exclusions" = 2, "Demographics Exclusions" = 7))
```

@@

>>>>

```{r setup, include = FALSE, cache=F}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("irr")
require(agreement)

@@

# set the default ggplot theme 
theme_set(theme_classic())

@@

```{r get exclusions data, include = F, cache = T}
df.excl_US <- read.csv("../../../data/responding/dataUS_excl_metadata.csv")
df.excl_CN <- read.csv("../../../data/responding/dataCN_excl_metadata.csv")
df.excl_VN <- read.csv("../../../data/responding/dataVN_excl_metadata.csv")
```

@@

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap="Proportion of thematic responses by country."}

@@

<!-- #### Raw lexical co-occurrences -->

<!-- To test whether variation in lexical co-occurrence can explain differences in similarity judgments between US and Vietnam participants, we compare logistic mixed-effects regression models fit to the thematic responding data from each country separately. We first ask how well each corpus model (English, Vietnamese, or Mandarin) predicts similarity judgments by speakers of the corresponding language (US, Vietnam, or China). To do this, we use a mixed-effects logistic regression to predict triad responses (0=taxonomic or 1=thematic) with corpus prediction (proportion thematic co-occurrence or cosine distance) as a fixed effect and participant and triad as random effects. -->

<!-- ```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
<!-- # English  -->
<!-- fit.EN_US = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.EN_US) -->
<!-- fit.EN_US.anova = Anova(fit.EN_US, type = 3) -->

<!-- #Vietnamese -->
<!-- fit.VI_US = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.VI_US) -->
<!-- fit.VI_US.anova = Anova(fit.VI_US, type = 3) -->

<!-- #Mandarin -->
<!-- fit.ZH_US = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "US", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.ZH_US) -->
<!-- fit.ZH_US.anova = Anova(fit.ZH_US, type = 3) -->
<!-- ``` -->

<!-- ```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
<!-- # English  -->
<!-- fit.EN_VN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.EN_VN) -->
<!-- fit.EN_VN.anova = Anova(fit.EN_VN, type = 3) -->

<!-- #Vietnamese -->
<!-- fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.VI_VN) -->
<!-- fit.VI_VN.anova = Anova(fit.VI_VN, type = 3) -->

<!-- #Mandarin -->
<!-- fit.ZH_VN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.ZH_VN) -->
<!-- fit.ZH_VN.anova = Anova(fit.ZH_VN, type = 3) -->
<!-- ``` -->

<!-- ```{r CN responding predicted by each corpus model raw co-occurrences, warning=FALSE, include=F, cache = TRUE} -->
<!-- #English -->
<!-- fit.EN_CN = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.EN_CN) -->
<!-- fit.EN_CN.anova = Anova(fit.EN_CN, type = 3) -->

<!-- #Vietnamese -->
<!-- fit.VI_CN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.VI_CN) -->
<!-- fit.VI_CN.anova = Anova(fit.VI_CN, type = 3) -->

<!-- #Mandarin -->
<!-- fit.ZH_CN = glmer(responses_theme ~ theme_freq_prop_M + (1 | subject) + (1 | triad),  -->
<!--           data = df %>% filter(country == "China", !(triad %in% triads_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.ZH_CN) -->
<!-- fit.ZH_CN.anova = Anova(fit.ZH_CN, type = 3) -->
<!-- ``` -->

<!-- ```{r calculate range of beta statistics for lexical cooc, warning=F, include=F} -->
<!-- beta.single_corpus_freq <- c( -->
<!--   round(fixef(fit.EN_US)["theme_freq_prop_E"], 2), -->
<!--   round(fixef(fit.VI_US)["theme_freq_prop_V"], 2),  -->
<!--   round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2),  -->

<!--   round(fixef(fit.EN_CN)["theme_freq_prop_E"], 2), -->
<!--   round(fixef(fit.VI_CN)["theme_freq_prop_V"], 2),  -->
<!--   round(fixef(fit.ZH_CN)["theme_freq_prop_M"], 2),  -->

<!--   round(fixef(fit.EN_VN)["theme_freq_prop_E"], 2), -->
<!--   round(fixef(fit.VI_VN)["theme_freq_prop_V"], 2),  -->
<!--   round(fixef(fit.ZH_VN)["theme_freq_prop_M"], 2) -->

<!-- ) -->
<!-- ``` -->
<!-- We found that all corpora are significant predictors of all cultural context responding, with p < 0.05 and $\beta$ from `r # min(beta.single_corpus_freq)` to `r #max(beta.single_corpus_freq)`. (For a full report, see Appendix.) -->

<!-- This suggests a strong shared similarity signal across the languages. -->

<!-- #### Cosine distances of fastText word vectors -->

@@

### Is responding in each cultural context __best__ predicted by the corresponding corpus's lexical statistics, as opposed to the other two corpora?
Next, we directly compare the corpus models by including both as fixed effects in three mixed-effect regressions (predicting US, Vietnam and China responding) with the same random effects as above. In R syntax, the model is: response ~ corpus_English + corpus_Vietnamese + corpus_Mandarin + (1|triad) + (1|subject).

<!-- #### Raw co-occurrences  -->

<!-- ```{r Eng-Vie-Mand lexical co-occ predicting US, warning=FALSE, include=F, cache = TRUE} -->
<!-- # ADDITION: adding theme_freq_prop_M,  -->
<!-- #raw co-occurrences -->
<!-- #linear mixed model with ALL corpora as predictors for each population. -->
<!-- fit.ENVIZH_US = glmer(responses_theme ~  -->
<!--                       theme_freq_prop_E + theme_freq_prop_V + theme_freq_prop_M + -->
<!--                       (1 | subject) + (1 | triad),  -->
<!--                     data = df %>% filter(country == "US", !(triad %in% triads_omit)), -->
<!--                     family="binomial") -->
<!-- summary(fit.ENVIZH_US) -->
<!-- fit.ENVIZH_US.anova = Anova(fit.ENVIZH_US, type = 3) -->
<!-- fit.ENVIZH_US.anova -->
<!-- ``` -->
<!-- For US responding: only English (EN) corpus is a significant predictor. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`. -->

<!-- ```{r Eng-Vie-Mand lexical co-occ predicting VN, warning=FALSE, include=F, cache = TRUE} -->
<!-- fit.ENVIZH_VN = glmer(responses_theme ~  -->
<!--                       theme_freq_prop_V + theme_freq_prop_E + theme_freq_prop_M + -->
<!--                       (1 | subject) + (1 | triad),  -->
<!--                     data = df %>% filter(country == "Vietnam", !(triad %in% triads_omit)), -->
<!--                     family="binomial") -->
<!-- summary(fit.ENVIZH_VN) -->
<!-- fit.ENVIZH_VN.anova = Anova(fit.ENVIZH_VN, type = 3) -->
<!-- fit.ENVIZH_VN.anova -->
<!-- ``` -->
<!-- For Vietnam responding: only Mandarin (ZH) corpus is a significant predictor. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`.VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_VN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_VN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_VN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.  -->

<!-- ```{r Eng-Vie-Mand lexical co-occ predicting CN, warning=FALSE, include=F, cache = TRUE} -->
<!-- fit.ENVIZH_CN = glmer(responses_theme ~  -->
<!--                       theme_freq_prop_M + theme_freq_prop_E + theme_freq_prop_V + -->
<!--                       (1 | subject) + (1 | triad),  -->
<!--                     data = df %>% filter(country == "China", !(triad %in% triads_omit)), -->
<!--                     family="binomial") -->
<!-- summary(fit.ENVIZH_CN) -->
<!-- fit.ENVIZH_CN.anova = Anova(fit.ENVIZH_CN, type = 3) -->
<!-- fit.ENVIZH_CN.anova -->
<!-- ``` -->
<!-- For China responding: only Mandarin (ZH) corpus is a significant predictor. ZH corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`. EN corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.ENVIZH_CN)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.ENVIZH_CN.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ENVIZH_CN.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`.  -->

<!-- ```{r echo=FALSE, warning = FALSE, cache = TRUE, fig.cap = "Fixed effect sizes of each corpus when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."} -->
<!-- coeff_value_freq <- c(fixef(fit.ENVIZH_US)["theme_freq_prop_M"], -->
<!--                  fixef(fit.ENVIZH_US)["theme_freq_prop_E"],  -->
<!--                  fixef(fit.ENVIZH_US)["theme_freq_prop_V"], -->
<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_M"], -->
<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_E"], -->
<!--                  fixef(fit.ENVIZH_VN)["theme_freq_prop_V"],  -->
<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_M"], -->
<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_E"],  -->
<!--                  fixef(fit.ENVIZH_CN)["theme_freq_prop_V"]) -->

<!-- se_value_freq <- c(summary(fit.ENVIZH_US)$coef["theme_freq_prop_M", "Std. Error"],  -->
<!--               summary(fit.ENVIZH_US)$coef["theme_freq_prop_E", "Std. Error"], -->
<!--               summary(fit.ENVIZH_US)$coef["theme_freq_prop_V", "Std. Error"],  -->
<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_M", "Std. Error"],  -->
<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_E", "Std. Error"], -->
<!--               summary(fit.ENVIZH_VN)$coef["theme_freq_prop_V", "Std. Error"], -->
<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_M", "Std. Error"],  -->
<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_E", "Std. Error"], -->
<!--               summary(fit.ENVIZH_CN)$coef["theme_freq_prop_V", "Std. Error"]) -->

<!-- country_value <- c(rep("US", 3), -->
<!--                    rep("VN", 3), -->
<!--                    rep("CN", 3)) -->

<!-- corpus_value <- c(rep(c("ZH", "EN", "VI"), 3)) -->

<!-- df.USVNCN_coeffs_freq <- data.frame(country_value, corpus_value, coeff_value_freq, se_value_freq) %>% -->
<!--   mutate(corpus_value = factor(corpus_value, levels=c("ZH", "EN", "VI"))) -->

<!-- plot.coeffs_freq <- ggplot(data = df.USVNCN_coeffs_freq,  -->
<!--        mapping = aes(x = country_value, y = coeff_value_freq, fill = corpus_value)) + -->
<!--   geom_bar(position="dodge", stat="identity") + -->
<!--   geom_errorbar(aes(ymin= coeff_value_freq - se_value_freq, ymax = coeff_value_freq + se_value_freq), width=.2, -->
<!--                  position=position_dodge(.9)) + -->
<!--   labs(x = "Country", y = "Fixed effect size", fill = "Corpus") +  -->
<!--   scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) +  -->
<!--   scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) +  -->
<!--   ggtitle('a') -->

<!-- ``` -->

<!-- ```{r freq model comparison, include=FALSE, cache = TRUE} -->
<!-- fit.US_freq_compare = anova(fit.ENVIZH_US, fit.EN_US, type = 3) -->
<!-- fit.VN_freq_compare = anova(fit.ENVIZH_VN, fit.VI_VN, type = 3) -->
<!-- fit.CN_freq_compare = anova(fit.ENVIZH_CN, fit.ZH_CN, type = 3) -->
<!-- ``` -->

<!-- We observed some level of language specificity from this analysis. The English corpus is the only significant predictor for US responding, and the Mandarin corpus is the only significant predictor for China response. However, against our prediction, the Vietnamese corpus was not a significant predictor for Vietnam responding when other corpora were included. (Figure 2a). -->

<!-- <!-- Nonetheless, we found that language specificity alone does not explain our results. We used an ANOVA to compare the model with only the corresponding corpus, and the model with all 3 corpora for each cultural context. We found that in all three cases (US, China, Vietnam), adding the other two corpora produces a significantly better fit than the identical model without the additional corpora, and only the corresponding corpus included as a predictor (US response: $\chi^2$(`r fit.US_freq_compare["fit.ENVIZH_US", "Df"]`) = `r round(fit.US_freq_compare["fit.ENVIZH_US", "Chisq"], 2)`, p `r ifelse( fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.US_freq_compare["fit.ENVIZH_US", "Pr(>Chisq)"], 3)), "< .001")`; Vietnam response: $\chi^2$(`r fit.VN_freq_compare["fit.ENVIZH_VN", "Df"]`) = `r round(fit.VN_freq_compare["fit.ENVIZH_VN", "Chisq"], 2)`, p `r ifelse( fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VN_freq_compare["fit.ENVIZH_VN", "Pr(>Chisq)"], 3)), "< .001")`; China response: $\chi^2$(`r fit.CN_freq_compare["fit.ENVIZH_CN", "Df"]`) = `r round(fit.CN_freq_compare["fit.ENVIZH_CN", "Chisq"], 2)`, p `r ifelse( fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.CN_freq_compare["fit.ENVIZH_CN", "Pr(>Chisq)"], 3)), "< .001")`).   -->

#### Cosine distances of fastText word vectors

@@

plot.coeffs_cos <- ggplot(data = df.USVNCN_coeffs_cos, 
       mapping = aes(x = country_value, y = coeff_value_cos, fill = corpus_value)) +
  geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin= coeff_value_cos - se_value_cos, ymax = coeff_value_cos + se_value_cos), width=.2,
                 position=position_dodge(.9)) +
  scale_y_reverse() + 
  labs(x = "Country", y = "Fixed effect size", fill = "Corpus") + 
  scale_x_discrete(labels=c("CN" = "China", "US" = "US", "VN" = "Vietnam")) + 
  scale_fill_manual(values=c("#D63230", "#1C77C3", "#F39237")) + 
  ggtitle('b')
```

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env = "figure", fig.pos = "h", fig.width=2, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=1, fig.cap="Fixed effect sizes of each corpus lexical statistics (cosine distance proportion) when included as a predictor for China, US, and Vietnam responding, respectively. The English corpus is the best predictor for US response, and the Mandarin corpus is the best predictor for China response."}
#plot.coeffs_freq + 
  plot.coeffs_cos
```

@@

<!-- ```{r add linguistic model to Ji et al., include=FALSE} -->
<!-- # this is probably similar to Q3 -->
<!-- fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad),  -->
<!--                            data = df %>% filter(country != "Vietnam"),  -->
<!--                            family = "binomial") -->

<!-- fit.country_corpus = glmer(responses_theme ~ country + theme_cosine_prop_E + theme_cosine_prop_M + (1 | subject) + (1 | triad),  -->
<!--                            data = df %>% filter(country != "Vietnam"),  -->
<!--                            family = "binomial") -->

<!-- fit.add_corpus <- anova(fit.country, fit.country_corpus, type = 3) -->

<!-- ``` -->

<!-- Our approach would be to compare a model that only includes country (US or China) as a fixed effect with one that also includes English and Chinese corpus data. Our previous model with an intercept per subject and one per triad, as well as by-triad random slopes for country to account for variation in the country effect across triads fails to converge with the more complex model, so we include a simpler random effect structure with an intercept per subject and one per triad in both the basic and more complex model. We compare this model with an identical model but including Chinese and English corpus cosine distance proportion prediction. We found that adding English and Chinese corpus data produces a significantly better fit than the identical model without English and Chinese corpus data as predictors ($\chi^2$(`r fit.add_corpus["fit.country_corpus", "Df"]`) = `r round(fit.add_corpus["fit.country_corpus", "Chisq"], 2)`, p = < .001. This suggests that including corpus data would better model the cross-cultural differences in similarity judgment in this study as well as similar studies. -->

@@

```{r echo=FALSE, warning=FALSE, cache = TRUE, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap="Proportion of thematic responses by country."}
#show violin plot
ggplot(df.country_filler,
       mapping = aes(x = factor(country, levels=c("China", "US", "Vietnam")), 
                     y = word1_resp_percent, 
                     color = factor(country, levels=c("China", "US", "Vietnam")))) +
  geom_violin() +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") + 
  labs(y = "Proportion Word1 Chosen", 
       x = "Country", 
       color = "Country") + 
  scale_color_manual(values=c("#D63230", "#1C77C3", "#F39237"))
```

```{r warning=FALSE, include = F, cache = TRUE, fig.env="figure", fig.width=2, fig.height=2, paged.print=TRUE}
# df.country_sum <- df.country %>%
#   group_by(country) %>%
#   summarize(mean_theme_resp_percent = mean(theme_resp_percent), 
#             sd_theme_resp_percent = sd(theme_resp_percent))

@@

### Does lexical statistics for fillers predict responding in the corresponding cultural context?
Using the same model structure as Analysis 2 ()
<!-- #### Raw co-occurrences -->
<!-- ```{r US responding predicted by each corpus model raw co-occurrences for fillers, warning=FALSE,include = F} -->
<!-- # English  -->
<!-- fit.EN_US_filler = glmer(responses_word1 ~ word1_match_frequency_prop_E + (1 | subject) + (1 | cue),  -->
<!--           data = df.filler %>% filter(country == "US",  -->
<!--                                !(cue_id %in% fillers_omit)),  -->
<!--           family="binomial") -->
<!-- summary(fit.EN_US_filler) -->
<!-- fit.EN_US_filler.anova = Anova(fit.EN_US_filler, type = 3) -->

@@

<!-- ```{r include=FALSE, cache = TRUE} -->
<!-- fit.country_no_triad <- glmer(responses_theme ~ country + (1 | subject),  -->
<!--                               data = df_main_analysis,  -->
<!--                               family = "binomial") -->

<!-- fit.country = glmer(responses_theme ~ country + (1 | subject) + (country | triad),  -->
<!--                     data = df_main_analysis,  -->
<!--                     family = "binomial") -->
<!-- summary(fit.country) -->

<!-- fit.no_triad_compare <- anova(fit.country, fit.country_no_triad, type = 3) -->
<!-- ``` -->

<!-- There are some suggestions that the current approach can predict triad-specific cross-cultural effects. First of all, an ANOVA model comparison showed that adding a random effect term for varying slope by country and varying intercept by triad to the model produces a significant better fit than the identical model without this random effect term included as a predictor ($\chi^2$(`r fit.no_triad_compare["fit.country", "Df"]`) = `r round(fit.no_triad_compare["fit.country", "Chisq"], 2)`, p `r ifelse( fit.no_triad_compare["fit.country", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.no_triad_compare["fit.country", "Pr(>Chisq)"], 3)), "< .001")`) -->

@@

@@

```{r xtable, results ="asis"}
US_agr <- agreement::dim_icc(df_main_analysis %>% filter(country == "US"),
                             model = "2A",
                             type = "agreement",
                             unit = "average",
                             object = triad,
                             rater = subject,
                             score = responses_theme,
                             bootstrap = 0)

print(tab1, type="latex", comment = F, table.placement = "t", include.rownames = FALSE)
```

## 2. Supplemental for whether each corpus predicts similarity judgement in each cultural context
<!-- ### Lexical co-occurrence -->
<!-- For US responding: English (EN), Vietnamese (VI), and Mandarin (ZH) corpus are all significant predictors. EN corpus: $\beta$ = `r round(fixef(fit.EN_US)["theme_freq_prop_E"], 2)`, $\chi^2$(`r fit.EN_US.anova["theme_freq_prop_E", "Df"]`) = `r round(fit.EN_US.anova["theme_freq_prop_E", "Chisq"], 2)`, p `r ifelse( fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.EN_US.anova["theme_freq_prop_E", "Pr(>Chisq)"], 3)), "< .001")`. VI corpus: $\beta$ = `r round(fixef(fit.VI_US)["theme_freq_prop_V"], 2)`, $\chi^2$(`r fit.VI_US.anova["theme_freq_prop_V", "Df"]`) = `r round(fit.VI_US.anova["theme_freq_prop_V", "Chisq"], 2)`, p `r ifelse( fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.VI_US.anova["theme_freq_prop_V", "Pr(>Chisq)"], 3)), "< .001")`. ZH corpus: $\beta$ = `r round(fixef(fit.ZH_US)["theme_freq_prop_M"], 2)`, $\chi^2$(`r fit.ZH_US.anova["theme_freq_prop_M", "Df"]`) = `r round(fit.ZH_US.anova["theme_freq_prop_M", "Chisq"], 2)`, p `r ifelse( fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"] > 0.001, paste0("= ", round(fit.ZH_US.anova["theme_freq_prop_M", "Pr(>Chisq)"], 3)), "< .001")`. -->
